Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/results-type.tex
Wordsmithed

Based on our statistical models (later reported in Section \ref{sec:regression}), we observed that the largest effect stemmed from the type of data being shared. The most and least concerning data types are listed in Table \ref{top10-table}, and the full list of data can be seen in Appendix \ref{sec:data-appendix}.

>>>>

Based on our statistical models (later reported in Section \ref{sec:regression}), we observed that the largest effect on participants' VURs stemmed from the type of data being shared; data recipient and device type had weaker impacts on overall VURs. The most and least concerning data types are listed in Table \ref{top10-table}, and the full list of data can be seen in Appendix \ref{sec:data-appendix}.
